\mytitle{}

### 2019-05-14 paper/paper.tex
Final typo

We choose these potential values for $p$ to add complete filtering to a steady progression of rate-limiters (\SI{25}{\percent} increments for UDP traffic).
The outlier, $p=0.05$, corresponds to roughly a \SI{50}{\percent} rate reduction for TCP flows in our test topology.
This uneven spread of choices for $p$ allows light and heavy rate reduction to be applied to both congestion-aware and non-congestion-aware traffic as required.

>>>>

We choose these potential values for $p$ to add complete filtering to a steady progression of rate-limiters (\SI{25}{\percent} increments for UDP traffic).
The outlier, $p=0.05$, corresponds to roughly a \SI{50}{\percent} rate reduction for TCP flows in our test topology.
This uneven spread of choices for $p$ allows light and heavy rate reduction to be applied to both congestion-aware and congestion-unaware traffic as required.
